Supplemental Materials for: Meta-analytic approaches and effect sizes to account for ‘nuisance heterogeneity’ in comparative physiology

### 2021-10-08 supp.Rmd
Added new PRISMA
Updated PRISMA text

All title, abstract and full text screening was done by two people (DWAN and ML). Any disagreements were resolved by discussion to reach a consensus. Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction. We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2). Figure \@ref(fig:figS1) outlines our PRSIMA flowchart detailing the number of papers hit, their sources and how many records were excluded and included at each screening phase.

@@

img1 <- readPNG(here::here("figs", "PRISMA_diagram_v0.png"))

@@

table_s1 <- flextable(table)                                                                            %>% 
            flextable::compose(j = 1, part = "header", value = as_paragraph(as_b("Date")))              %>% 
            flextable::compose(j = 2, part = "header", value = as_paragraph(as_b("Search Number")))     %>% 
            flextable::compose(j = 3, part = "header", value = as_paragraph(as_b("Search String")))     %>% 
            flextable::compose(j = 4, part = "header", value = as_paragraph(as_b("Number of Records"))) %>% 
            flextable::compose(j = 5, part = "header", value = as_paragraph(as_b("Comments")))          %>% 
            flextable::compose(j = 6, part = "header", value = as_paragraph(as_b("Notes"))) 
 table_s1
```

>>>>

All title, abstract and full text screening was done by two people (DWAN and ML). Any disagreements were resolved by discussion to reach a consensus. Out of the 426 papers originally identified, 80 full texts were screened for eligibility, and we included a total of 63 for final data extraction. We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2). Figure \@ref(fig:figS1) outlines our PRSIMA flowchart detailing the number of papers hit, their sources and how many records were excluded and included at each screening phase.

@@

img1 <- readPNG(here::here("figs", "PRISMA_diagram_v1.png"))

@@

table_s1 <- flextable(table)                                                                            %>% 
            flextable::compose(j = 1, part = "header", value = as_paragraph(as_b("Date")))              %>% 
            flextable::compose(j = 2, part = "header", value = as_paragraph(as_b("Search Number")))     %>% 
            flextable::compose(j = 3, part = "header", value = as_paragraph(as_b("Search String")))     %>% 
            flextable::compose(j = 4, part = "header", value = as_paragraph(as_b("Number of Records"))) %>% 
            flextable::compose(j = 5, part = "header", value = as_paragraph(as_b("Comments")))          %>% 
            flextable::compose(j = 6, part = "header", value = as_paragraph(as_b("Notes"))) %>% 
  width(j = 3, 8)
 table_s1
```
